Robots, Are They Overlords or Serf-Laborers?

### 2015-06-10 draft1.tex
Merge two papers cohessively

\note{First Draft; 6/8/2015}

@@

\subsection{v1}
Although AI is a research topic in the fields of engineering and science, the first introduction of it was fictional literary and futuristic artistic works. For that reason, its popularity significantly ascended which resulted in becoming perhaps the most debated technology related term in the last century. Despite AI's popularity, it may be the most misunderstood term that in the field of engineering. In order to make clear its obfuscated definition, the tasks of AI should be mentioned. The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion. The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making. Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI. Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.
\subsection{v2}

@@

@@

>>>>

\note{First Draft; 6/8/2015; \LaTeX}

@@

@@

One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI. Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.\par

@@

% A strip from the old paper
In order to make clear its obfuscated definition, the tasks of AI should be addressed. The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion. The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making. Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
